\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-17 manuscript.Rmd
Chunks renamed,clutter free snapshot

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Helvetica")
```

```{undefined eval=FALSE, include=FALSE}
library(packrat)
#This chunk is disabled. Only run this to install the dependencies automatically.
packrat::init()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

```{r eval=FALSE, include=FALSE}
#if "packrat" does not work you can run this chunk manually to get all required packs"

@@

```{r setup, include=FALSE}

@@

```{=html}
<!-- -->
```
    \newpage
    \begin{landscape}

@@

    \end{landscape}

@@

```{r preparingData, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

@@

```{r descriptives, eval=FALSE, include=FALSE}
#Use these  data frames for descriptive
EFA.descriptives #Only EFA, n =428
CFA.descriptives #Only CFA, n =262  
descriptives.data# Total sample, n = 690

@@

```{r flowchart, include=FALSE }
Flowchart1 <- grViz("digraph nicegraph{

@@

@@

```{r CorrelationMatrix, include=FALSE}
#Polychoric Correlation matrix

@@

```{r figCor,out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r Parallel, include=FALSE}

@@

apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'))

@@

```{r Hull, include=FALSE}
# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ theme(panel.grid.major = element_blank(),
                                               panel.grid.minor = element_blank(),
                                               panel.background = element_blank(),
                                               axis.line.x = element_line(color='black'),
                                               axis.line.y = element_line(color='black'))

```{r MAP, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```

@@

```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'),ncol=1, label_size = 8)

@@

```{r TabEFA5, results='asis'}

apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "tiny")
```

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

>>>>

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Helvetica")
```

```{r depMan, eval=FALSE, include=FALSE}
library(packrat)
#This chunk is disabled. Only run this to install the dependencies automatically.
packrat::init()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

```{r install, eval=FALSE, include=FALSE}
#if "packrat" does not work you can run this chunk manually to get all required packs"

@@

```{r library, include=FALSE}

@@

@@

@@

```{r Data, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

@@

@@

```{r Manuflowchart, include=FALSE }
Flowchart1 <- grViz("digraph nicegraph{

@@

```{r ggplot2, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        text=element_text(family = "Helvetica",),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

```{r CorrMatrix, include=FALSE}
#Polychoric Correlation matrix

@@

```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r ParallelEFA, include=FALSE}

@@

@@

```{r HullEFA, include=FALSE}
# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
```

```{r MAPefa, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```

@@

```{r facIdFig, out.height="120%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

```{r EFATable, results='asis'}

apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
```

```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
